---
title: "Exploring mtcars"
author: "Mohamad Barad"
date: "06-02-2022"
output: ioslides_presentation
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)

# Loading packages
library(plotly)
```

## Introduction
This presentation should supplement the project thereby giving a summary of one of the models that could be obtained in the shiny application
First, the shiny application could be developed much more, with this examples of further development include

- Including tabs
- Including summary tables
- Working on labels and legends  
- Adding the summary of the fitted model
- Using new data to predict new values 
- Etc. 

## mtcars data set
So the data set explored in the shiny application was 'mtcars'
```{r mtcars, echo = TRUE}
# taking a look on the top of mtcars data set
head(mtcars)

```

## Plotting {.smaller}
Here mpg is a function of hp and cyl

```{r plot, echo = TRUE,fig.height=4}
plot_ly(mtcars, x= ~hp, y=~mpg , color = ~as.factor(cyl), 
        type = "scatter", mode= "markers")
```

## lm model output {.smaller}
```{r model, echo=TRUE}
# fitting a linear model
fit <- lm(mpg ~ hp , mtcars)
# Looking at the summary 
summary(fit)
```

